---
title: "Sea_Cucumber_Wasting_JF_DT_Dec2021"
author: "Jonathan Farr and Declan Taylor"
date: "12/12/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in our datafiles

Reading in packages used for data cleaning/sorting: 
```{r}
library(here)
library(lubridate)
library(tidyverse)
```


## Longitudinal temperature data for figure 4
```{r, warning=FALSE, message = FALSE}

# Importing data and formatting the date/time information.
DailyLog <- read_csv("data/DailyLog.csv", col_names = TRUE) %>%
  # Format `Date` column to POSIX standard
  mutate("Date" = dmy(Date)) %>%
  # Create column with date and time info
  mutate("dateTime" = paste(Date, Time, sep = "_")) %>%
  # Format `dateTime` to POSIX standard
  mutate(dateTime = ymd_hms(dateTime)) %>%
  # Make `Sea_Table` and `Bucket_ID` factorial data.
  mutate(Sea_Table = as.factor(Sea_Table),
         Bucket_ID = as.factor(Bucket_ID)) %>%
  # Renaming!
  select(date = Date,
         date_time = dateTime,
         sea_table = Sea_Table,
         table_position,
         bucketID = Bucket_ID,
         cukeID = Cuke_ID,
         treatment = Treatment,
         temp_C = Temp_C,
         alive = Alive,
         death_time = `Time of Death`,
         poop = Poop,
         evisceration = Evisceration,
         resp_evisc = respiratory_evisceration,
         spawn = Spawn) %>%
  mutate(tableID = paste(sea_table, table_position)) %>%
  tail(-34)

# Making a new dataframe to get some values about the range and variation in our
# temperature data.
tempRange <- DailyLog %>%
  filter(date == "2021-11-11" | date == "2021-11-12") %>%
  select(date, date_time, tableID, treatment, temp_C) 

# Generating a list of the times at which the 5 cucumbers died.
death_time <- DailyLog %>%
  # Filter for rows with death data
  filter(FALSE == is.na(alive) | FALSE == is.na(death_time)) %>%
  # Use POSIXct standard for death_time
  mutate(death_time = ymd_hms(paste(date, death_time))) %>%
  select(death_time, bucketID, temp_C) %>%
  mutate(placehold = 1)

# Generating a dataframe for the temperature data over time so that we can
# create a plot.
Temp_Time <- DailyLog %>%
  select(date_time, date, sea_table, table_position, bucketID, tableID, temp_C)

```


## Binary data for analyses and figures related to mortality, spawning, ulcers and evisceration 
Functions that generate data frames withdeath_time, spawning, evisceration, and poop data. 
The function exists so the dataframe can be  easily made in one click.
```{r, warning=FALSE, message=FALSE}
create_individualData <- function(datafile){
  # Import Data
  DailyLog <- read_csv(here(paste0("data/", datafile)), col_names = TRUE) %>%
    # Format `Date` column to POSIX standard
    mutate("Date" = dmy(Date)) %>%
    mutate("dateTime" = paste(Date, Time, sep = "_")) %>%
    mutate(dateTime = ymd_hms(dateTime))
  
  # Generate data frame to hold just the binary variables. Upper limit of 
  # dataframe is intentionally too big (I'm just removing the top 35 rows).
  SelectedData <- DailyLog %>%
    # remove the first 34 lines of data frame (pre-experiment data).
    tail(-34) %>%
    # Select and rename variables
    select(date = Date,
           date_time = dateTime,
           sea_table = Sea_Table,
           table_position,
           bucketID = Bucket_ID,
           cukeID = Cuke_ID,
           treatment = Treatment,
           temp_C = Temp_C,
           alive = Alive,
           death_time = `Time of Death`,
           poop = Poop,
           evisceration = Evisceration,
           resp_evisc = respiratory_evisceration,
           spawn = Spawn) %>%
    # Generate a `combinedID` from bucketID (1-30) and cukeID (A or B), which is 
    # unique to each individual cucumber in the study.
    mutate(combinedID = paste(bucketID, cukeID),
           tableID = paste(sea_table, table_position))
  
  # For each individual-level variable, create a dataframe that selects only
  # the rows for which that variable's column has data. Each dataframe is named
  # after the variable it represents.
  # Format that data to change all the values to "1". Select only the 
  # combinedID and <variable> columns, and keep only the distinct combinedID
  # values. This effectively generates a list of cucumbers in which the
  # <varible> process (i.e. pooping) occurred.
  death_time <- SelectedData %>%
    # Filter for rows with death data
    filter(FALSE == is.na(alive) | FALSE == is.na(death_time)) %>%
    # Use POSIXct standard for death_time
    mutate(death_time = ymd_hms(paste(date, death_time))) %>%
    select(death_time, combinedID)
  
  evisceration <- SelectedData %>%
    filter(FALSE == is.na(evisceration)) %>%
    # sub text entries like "yes" for `1`.
    mutate(evisceration = gsub("[A-z]{3}", 1, evisceration))%>%
    select(combinedID, evisceration) %>%
    distinct(combinedID, .keep_all = TRUE)
  
  resp_evisc <- SelectedData %>%
    filter(FALSE == is.na(resp_evisc)) %>%
    mutate(resp_evisc = gsub("[A-z]{3}", 1, resp_evisc))%>%
    select(combinedID, resp_evisc) %>%
    distinct(combinedID, .keep_all = TRUE)
  
  poop <- SelectedData %>%
    filter(FALSE == is.na(poop)) %>%
    mutate(poop = gsub("[A-z]{3}", 1, poop)) %>%
    select(combinedID, poop) %>%
    distinct(combinedID, .keep_all = TRUE)
  
  spawn <- SelectedData %>%
    # text entries may be "yes" or "eggs".
    mutate(spawn = gsub("[A-z]{3,4}", 1, spawn, ignore.case = TRUE)) %>%
    filter(FALSE == is.na(spawn)) %>%
    select(combinedID, spawn) %>%
    distinct(combinedID, .keep_all = TRUE)
  
  # List the variables for which dataframes were created.
  SelectedVariables <- c("death_time", "evisceration", "resp_evisc", "poop", "spawn")
  
  # Generate a 1-column data frame which is a list of all the combinedID values
  # (i.e. all the unique bins in our experiment).
  IndividualData <- SelectedData %>%
    select(date_time,
           tableID,
           bucketID,
           cukeID,
           combinedID,
           treatment) %>%
    distinct(combinedID, .keep_all = TRUE) %>%
    drop_na()
  
  # For each of the individual data frames made above, join the `1` data 
  # (selected occurance data) to the 1-column dataframe  for only the values 
  # with 1s. The rest are left as NAs.
  for(i in SelectedVariables) {
    variable <- get(i)
    IndividualData <- full_join(IndividualData, variable, by = "combinedID")
    
    IndividualData[,i] <- IndividualData[,i] %>%
      replace_na()
  }

  # Replace NA values with 0s and make each column numberic; turns each binary
  # response variable into a binary data column with 0s and 1s.
  IndividualData$evisceration <- IndividualData$evisceration %>% 
    replace_na(0) %>%
    as.numeric(IndividualData$evisceration)
  IndividualData$resp_evisc <- IndividualData$resp_evisc %>% 
    replace_na(0) %>%
    as.numeric(IndividualData$resp_evisc)
  IndividualData$poop <- IndividualData$poop %>% 
    replace_na(0) %>%
    as.numeric(IndividualData$poop)
  IndividualData$spawn <- IndividualData$spawn %>% 
    replace_na(0) %>%
    as.numeric(IndividualData$spawn)
  
  # Fix data types to factors and assign IndividualData to the global environment
  IndividualData <<- IndividualData %>%
    mutate(treatment = as.factor(treatment),
           cukeID = as.factor(cukeID),
           poop = as.factor(poop),
           tableID = as.factor(tableID),
           bucketID = as.factor(bucketID))
}

# This function generates a dataframe stress scores and
# joins said dataframe to the 'master' IndividualData dataframe.
add_stressData <- function(datafile){
  # Import data
  StressData <- read_csv(here(paste0("data/", datafile)), col_names = TRUE) %>%
    # Format `Date` column to POSIX standard
    mutate("Date" = dmy(Date)) %>%
    mutate("dateTime" = paste(Date, Time, sep = "_")) %>%
    mutate(dateTime = ymd_hms(dateTime)) %>%
    select(date = Date,
           time = Time,
           date_time = dateTime,
           sea_table = Sea_Table,
           table_position = Table_Position,
           bucketID = Bucket_ID,
           cukeID = Cuke_ID,
           treatment = Treatment,
           activity = Activity_Score,
           squeeze = Squeeze_score,
           droop = Droop_score) %>%
    mutate(combinedID = paste(bucketID, cukeID))
  
  # Generate initial data values for droop and squeeze based on the 
  # readings taken on the first day of the experiment.
  initial_stress_values <- StressData %>%
   # dplyr method of doing: filter(date_time == "2021-11-09 09:40:00") 
    mutate(date = as.character(date),
           time = as.character(time)) %>%
    filter(date == "2021-11-09" & 
           time == "09:40:00") %>%
    # Make droop and squeeze data factorial
    mutate(droop = as.factor(droop),
           squeeze = as.factor(squeeze)) %>%
    # Columns to be added to IndividualData, with droop and squeeze indicated
    # as initial data.
    select(combinedID,
           in_activity = activity,
           in_droop = droop,
           in_squeeze = squeeze)
  
  IndividualData <<- full_join(IndividualData, initial_stress_values, by = "combinedID")
}

# This function adds weight data to the master IndividualData dataframe.
add_weightData <- function(datafile){
  WeightData <- read_csv(here(paste0("data/", datafile)), col_names = TRUE) %>%
    mutate(combinedID = paste(Bucket_ID, Cuke_ID)) %>%
    # Create an average weight from the two weight measurements taken at the 
    # start of teh experiment.
    mutate(weight_g = (Weight_g + Weight_2)/2) %>%
    select(weight_g, combinedID)
  
  # Join the weight data to the full dataframe.
  IndividualData <<- full_join(IndividualData, WeightData, by = "combinedID")
}

```

Now, we run all three functions once, sequentially
Returned data frame should have 16 variables across. 
IndividualData df is the desired output

```{r, warning=FALSE, message=FALSE}
create_individualData("DailyLog_final.csv")
add_stressData("BehaviourData_final.csv")
add_weightData("SizeData.csv")
```

## Second, we read in longitudinal data frames with behaviours measured over time 
This data will later be used for stiffness analysis
```{r,, warning=FALSE, message=FALSE}
behav = read_csv("data/BehaviourData_Final.csv") %>% 
  mutate(
         Treatment=fct_relevel(Treatment, c("Control","Room","Heat")),
         Bucket_ID = as.factor(Bucket_ID),
         Cuke_ID=as.factor(Cuke_ID),
         Unique_ID=paste(Bucket_ID, Cuke_ID,  sep = '_'), 
         Table_ID = paste(Sea_Table, Table_Position, sep='_'), 
         Date = as.Date(Date, format="%d-%m-%Y")) %>%
  dplyr:: select(-c(Sea_Table, Table_Position))

```

## Data for ulcer analysis
```{r, warning=FALSE, message=FALSE}
lesion = read_csv("data/BehaviourData_Final.csv") %>%
  mutate(
    Treatment=fct_relevel(Treatment, c("Control","Room","Heat")),
    Bucket_ID = as.factor(Bucket_ID),
    Cuke_ID=as.factor(Cuke_ID),
    Unique_ID=paste(Bucket_ID, Cuke_ID,  sep = '_'), 
    Table_ID = paste(Sea_Table, Table_Position, sep='_'), 
    Date = as.Date(Date, format="%d-%m-%Y")) %>%
  dplyr:: select(c(Unique_ID, Bucket_ID, Table_ID, Date, Treatment, Number_lesions)) %>%
  na.omit()


# find max number of lesions per individual
lesion_max = lesion %>%
  group_by(Unique_ID) %>%
  mutate(max_lesions = max(Number_lesions)) %>%
  distinct(Unique_ID, .keep_all=TRUE) %>%
  dplyr::select(-"Number_lesions")

# reading in weight data
size = read_csv("data/SizeData.csv") %>%
  mutate(
    Bucket_ID = as.factor(Bucket_ID),
    Cuke_ID=as.factor(Cuke_ID),
    Unique_ID=paste(Bucket_ID, Cuke_ID,  sep = '_'),
    mean_weight = (Weight_g+Weight_2)/2) %>%
  dplyr::select(c(Unique_ID, mean_weight))

# adding weight data to lesion data (using IndividualData)
individual_pooping = IndividualData %>%
  mutate(Unique_ID = paste(bucketID, cukeID, sep="_"))%>%
  select(c("Unique_ID", "poop", "evisceration"))


lesion_max = merge(lesion_max, individual_pooping, by=c("Unique_ID"))
lesion_max = merge(lesion_max, size, by=c("Unique_ID"))

```


## Data for mortality analysis = DeathData
```{r, warning=FALSE, message=FALSE}
# Restrict the IndividualData dataframe just to cucumbers that had a comment
# in the death column (only done for cucumbers that died).
DeathData <- IndividualData %>%
  dplyr::mutate(death_time = gsub(".{1,}", 1, death_time)) %>%
  dplyr::select(-in_activity)

# Replace NA values in the death_time colum with 0s.
DeathData$death_time <- DeathData$death_time %>% 
  replace_na(0) %>%
  as.numeric(IndividualData$death_time)

DeathData <- DeathData %>%
  rename("death" = death_time)

```

## Data for stiffness = stiff
```{r, warning=FALSE, message=FALSE}
stiff = behav %>%
  dplyr::select(-c(Activity_Score, Number_lesions, 'Bodywall lesions')) %>%
  na.omit()

```


## Data for spawning = spawnData

```{r, warning=FALSE, message=FALSE}

# This function generates a dataframe that our spawning statistical analysis 
# uses. `dplyr` functions that conflict with other packages are captioned 
# explicity .
create_spawnData <- function(datafile){
  SelectedData <- read_csv(here(paste0("data/", datafile)), col_names = TRUE) %>%
    # Format `Date` column to POSIX standard
    dplyr::mutate("Date" = dmy(Date),
                  "dateTime" = paste(Date, Time, sep = "_"),
                  dateTime = ymd_hms(dateTime))
  
  SelectedData <- SelectedData %>%
    # remove the first 34 lines of data frame (improperly formatted 
    # pre-experiment data).
    tail(-34) %>%
    # Select and rename variables
    dplyr::select(date = Date,
                 date_time = dateTime,
                 sea_table = Sea_Table,
                 table_position,
                 bucketID = Bucket_ID,
                 cukeID = Cuke_ID,
                 treatment = Treatment,
                 temp_C = Temp_C,
                 alive = Alive,
                 death_time = `Time of Death`,
                 poop = Poop,
                 evisceration = Evisceration,
                 resp_evisc = respiratory_evisceration,
                 spawn = Spawn) %>%
    # replace any word such as "Yes", "yes", "egg", or "Eggs" in the spawn 
    # column with a `1`.
    dplyr::mutate(spawn = gsub("[A-z]{3,4}", 1, spawn, ignore.case = TRUE))
  
  # Select only buckets and spawn (`1`) data for those buckets that spawned.
  spawnData <- SelectedData %>%
    dplyr::filter(FALSE == is.na(spawn)) %>%
    dplyr::select(bucketID, spawn) %>%
    distinct(bucketID, .keep_all = TRUE)
  
  # Generate a list (1-col dataframe) with all of the buckets (bins) in the 
  # experiment listed by their ID numbers.
  bucketList <- SelectedData %>% 
    dplyr::select(bucketID, treatment) %>%
    distinct(bucketID, .keep_all = TRUE) %>%
    drop_na()
  
  # Join the spawn information (`1`) counts with the total list of all buckets
  # to create a dataframe of 1s and 0s of spawn data.
  spawnData <- full_join(bucketList, spawnData, by = "bucketID") %>%
    dplyr::mutate(spawn = as.numeric(spawn))
  spawnData$spawn <- replace_na(spawnData$spawn, 0)
  
  # Save this dataframe to the RStudio global environment.
  spawnData <<- spawnData
}

# This function is exactly the same as the above, but the regular expressions
# are slightly adjusted to only pick up sperm data instead of sperm and egg 
# spawning.
create_spermData <- function(datafile){
  
  SelectedData <- read_csv(here(paste0("data/", datafile)), col_names = TRUE) %>%
    dplyr::mutate("Date" = dmy(Date)) %>%
    dplyr::mutate("dateTime" = paste(Date, Time, sep = "_")) %>%
    dplyr::mutate(dateTime = ymd_hms(dateTime))
  
  SelectedData <- SelectedData %>%
    tail(-34) %>%
    dplyr::select(date = Date,
                  date_time = dateTime,
                  sea_table = Sea_Table,
                  table_position,
                  bucketID = Bucket_ID,
                  cukeID = Cuke_ID,
                  treatment = Treatment,
                  temp_C = Temp_C,
                  alive = Alive,
                  death_time = `Time of Death`,
                  poop = Poop,
                  evisceration = Evisceration,
                  resp_evisc = respiratory_evisceration,
                  spawn = Spawn) %>%
    # Note the regular expressions, which must start with [Y, y], and must be
    # 3 total characters.
    dplyr::mutate(spawn = gsub("y[A-z]{2}", 1, spawn, ignore.case = TRUE))
  
  spawnData <- SelectedData %>%
    dplyr::filter(FALSE == is.na(spawn)) %>%
    dplyr::select(bucketID, spawn) %>%
    distinct(bucketID, .keep_all = TRUE)
  
  bucketList <- SelectedData %>% 
    dplyr::select(bucketID, treatment) %>%
    distinct(bucketID, .keep_all = TRUE) %>%
    drop_na()
  
  spawnData <- full_join(bucketList, spawnData, by = "bucketID") %>%
    dplyr::mutate(spawn = as.numeric(spawn))
  spawnData$spawn <- replace_na(spawnData$spawn, 0)
  
  spermData <<- spawnData
}

# Running the 2 functions above to generate the dataframes required to run the 
# statistics below.
create_spawnData("DailyLog_final.csv")
create_spermData("DailyLog_final.csv")
```


## Data for evisceration = EviscData
```{r, warning=FALSE}
# Drop the final row (all NAs) and the death_time and in_activity columns 
# (contain NAs) from `IndividualData`, so we can use gamlss models.
EviscData <- IndividualData %>%
  dplyr::select(-c(death_time, in_activity, in_droop, in_squeeze))

```


\newpage


# Running analyses 
Now, we use our data frames generated above to conduct analyses on our data 
First - load in the packages used for analyses
```{r, warning=FALSE, message=FALSE}
library(gamlss)
library(FSA)
library(ordinal)
library(MuMIn)
library(FSA)
library(Hmisc)

```


## Temperature trends 
making sure that temps were different in our treatments
```{r, warning=FALSE}
# Investigating the range and average temperatures of our 3 treatments.

# 12C
range(subset(tempRange, treatment=="control")$temp_C)
mean(subset(tempRange, treatment=="control")$temp_C)

# 17C
range(subset(tempRange, treatment=="room")$temp_C) 
mean(subset(tempRange, treatment=="room")$temp_C)

# 22C
range(subset(tempRange, treatment=="heat")$temp_C) 
mean(subset(tempRange, treatment=="heat")$temp_C)

```


## Ulcer Statistics
Conducting regression analyses for differences in minor ulcers across temperature treatments
```{r, warning=FALSE}
# we are using the data frame lesion_max
# which denotes the maximum number of ulcers per individual cucumber

# finding the distribution that best fits our response variable (max_lesions)
gamlss::fitDist(max_lesions, data=lesion_max, type="counts", try.gamlss=TRUE)
# geometric distribution is best (woohoo!)

# creating a full model 
ulcers_Full_model =gamlss(max_lesions ~ mean_weight + Treatment + poop + evisceration+
                      random(as.factor(Table_ID)) + random(as.factor(Bucket_ID)),
                      family = GEOM(), data = lesion_max)

#backward model selection to find top model
step.lesions.backward <- stepGAIC(ulcers_Full_model, 
                              direction = "backward", trace = F)
summary(step.lesions.backward) # null model is best fit

```



## Mortality Statistics
Using a kruskal-wallis test to examine differences in mortality across temperature treatments
We also used logistic regression to test for within-treatment factors affecting survival 
```{r, warning=FALSE}

# Statistics! First, kruskal-wallis test
kruskal.test(death ~ treatment, data = DeathData)
# p-value = 0.003374
# second, Dunn Test for pairwise comparisons
FSA::dunnTest(death ~ treatment, data = DeathData)

# We looked at what non-treatment factors affected death to learn more about 
# what may increase a heated cucumber's chance of death.
# Full model, no random effects. BI() used as family as death is represented by
# a 1, and survival a 0. Respiratory evisceration is omitted because all those
# that eviscerated their respiratory tree died.
death.mod.full <- gamlss(death ~ evisceration + poop + in_droop + in_squeeze + weight_g,
                    family = BI(),
                    data = DeathData)

# Forwards selection.
backward.death.mod <- stepGAIC(death.mod.full, 
                          direction = "backward", 
                          trace = F)
# Checking out the model output:
formula(backward.death.mod)
## death ~ 1
summary(backward.death.mod)
## null model is best explanation!
```


## Stiffness Statistics
First, we examine the correlation between the two stiffness scores with rcorr. 
Then, we use clmm() from ordinal package to analyze data
We also use dredge from MuMIn to do model selection (code not run because of long processing times)
** Droop = structural maintenance, Squeeze = antipredator**
```{r, warning=FALSE}
# examining correlation between droop and squeeze
Hmisc::rcorr(stiff$Squeeze_score,stiff$Droop_score, type="spearman") 

# only include dates from Nov 9 to Nov 13
# aka the day before, days during, and day after the heat treatment
stiff_heat = subset(stiff, Date < "2021-11-14")

# full model for squeeze score
Squeeze_Full = ordinal::clmm(as.factor(Squeeze_score)~ Treatment + as.factor(Date) + Treatment*as.factor(Date) + 
                   (1|Unique_ID) + (1|Bucket_ID) + (1|Table_ID), na.action="na.fail",
                 data = stiff_heat) 

# model selection code, not run because of processing time
# dredge.Squeeze <- MuMIn::dredge(Squeeze_Full) 
# view(dredge.Squeeze) # top model does not include interaction term

# top squeeze model 
Squeeze_Top = ordinal::clmm(as.factor(Squeeze_score)~ Treatment + as.factor(Date) +
                   (1|Unique_ID) + (1|Bucket_ID) + (1|Table_ID), na.action="na.fail",
                 data = stiff_heat) 
summary(Squeeze_Top)

## full model for droop score
Droop_Full = ordinal::clmm(as.factor(Droop_score)~ Treatment + as.factor(Date) + Treatment*as.factor(Date)+
                      (1|Unique_ID) +(1|Bucket_ID)+(1|Table_ID), na.action="na.fail",
                    data = stiff_heat) 

# model selection code, not run because of processing time
#dredge.Droop <- MuMIn::dredge(Droop_Full) 
#view(dredge.Droop) # again, top model does not include interaction term 

# top model for droop score
Droop_Top = ordinal::clmm(as.factor(Droop_score)~ Treatment + as.factor(Date) + 
                      (1|Unique_ID) +(1|Bucket_ID)+(1|Table_ID), na.action="na.fail",
                    data = stiff_heat) 
summary(Droop_Top)
```

## Spawning Statistics
To look at per-bucket spawning we simply use KW tests and observed no differences
```{r, warning=FALSE}
# Find the number of cucumber bins that spawned.
sum(spawnData$spawn)
# 11 bins spawned.

# Statistics on spawn data as a whole.
kruskal.test(spawn ~ treatment, data = spawnData)
FSA::dunnTest(spawn ~ treatment, data = spawnData)
# p = 0.379
```


## Evisceration Statistics
We model the effect of treatment, weight, and guts status, along with random effects, on evisceration

```{r, warning=FALSE}
sum(EviscData$evisceration)
# N = 12 eviscerated <- should be n=13

# full model for evisceration
evisc.mod.full <- gamlss(evisceration ~ 
                           treatment + weight_g + poop + bucketID +
                           random(tableID),
                         family = BI(),
                         data = EviscData)

# backward model selection
backward.evisc.mod <- stepGAIC(evisc.mod.full,
                              direction = "backward", 
                              trace = F)
formula(backward.evisc.mod)
## evisceration ~ poop + weight_g
summary(backward.evisc.mod)
# poop (p = 0.0163) and weight (p = 0.0383) are both significant in explaining 
# variation in evisceration. Weight estimate = -0.004309.

```

\newpage

# Figures


## Figure 3 - temperature trends
```{r, warning=FALSE}

TempPlot <- ggplot(data = Temp_Time,
            aes(x = date_time,
                y = temp_C,
                # Ignore warning about 'unknown aesthetic'... this code is 
                # still important and functioning!
                fill = bucketID)) +
  geom_line(color="black")+
  scale_x_datetime(date_breaks = "1 day", date_labels = "%b %d") +
  geom_hline(aes(yintercept = 22,  
             colour = "22°C"),
             size = 1,
             alpha = 0.8) +
  geom_hline(aes(yintercept = 17,
             colour = "17°C"),
             size = 1,
             alpha = 0.8) +
  geom_hline(aes(yintercept = 12,
             colour = "12°C"),
             size = 1,
             alpha = 0.8) +
  labs(x = "Date",
       y = "Temperature (°C)",
       colour = "Treatment Temperature") +
  scale_colour_manual(values = c("Gold", "Orange","Red")) +
    guides(colour = guide_legend(reverse = TRUE)) +
  scale_y_continuous(breaks = c(12, 14, 16, 18, 20, 22, 24))+
  theme_bw()+ 
  theme(panel.grid=element_blank())

ggsave("Fig3_temp_plot.png", TempPlot, device = "png", path = here("figures"), width=8, height=5)
```

## Figure 4 and 5 Stiffness
Figure 4 = antipredator stiffness
Figure 5 = structural stiffness

```{r, warning=FALSE}
# making data for plotting 
stiff_plot = stiff %>%
  dplyr::mutate(Squeeze_score = as.factor(Squeeze_score),
         Droop_score = as.factor(Droop_score)) %>%
  dplyr::filter(Date != "2021-11-14")

# making vector with facet labels
facet.labs=c("12°C", "17°C", "22°C")
names(facet.labs)=c("Control", "Room", "Heat")

# FIGURE 4
# plotting antipredator response 
squeeze_plot = 
  ggplot(data =stiff_plot, aes(x=as.factor(Date), fill=Squeeze_score))+
  geom_bar(alpha=0.8, color="black", size=0.5) +
  scale_x_discrete(breaks=c("2021-11-09","2021-11-10","2021-11-11", "2021-11-12","2021-11-13","2021-11-15", "2021-11-20"),
                   labels=c(1,2,3,4,5,7,12))+
  xlab("Experiment Day") + ylab("Number of Sea Cucumbers")+
  geom_vline(xintercept=1.5, linetype=2, size=1)+ geom_vline(xintercept=4.5, linetype=2, size=1)+
  scale_y_continuous(expand=c(0,0))+
  scale_fill_manual(name="Antipredator Stiffness",labels=c("0 - Soft","1 - Standard","2 - Stiff"), values=c("burlywood4", "tan", "beige"))+ 
  theme_bw()+
  theme(strip.text.y = element_text(size =12),
        panel.grid=element_blank(),
        legend.position="right")+
  facet_grid(Treatment~.,labeller=labeller(Treatment = facet.labs))

ggsave("figures/Fig4_antipredator_stiffness.jpg",plot=squeeze_plot, width=6, height=5)

# FIGURE 5
# plotting structural maintenance
droop_plot = 
  ggplot(data =stiff_plot, aes(x=as.factor(Date), fill=Droop_score))+
  geom_bar(alpha=0.8, color="black", size=0.5) +
  scale_x_discrete(breaks=c("2021-11-09","2021-11-10","2021-11-11", "2021-11-12","2021-11-13","2021-11-15", "2021-11-20"), labels=c(1,2,3,4,5,7,12))+
  xlab("Experiment Day") + ylab("Number of Sea Cucumbers")+
  geom_vline(xintercept=1.5, linetype=2, size=1)+ geom_vline(xintercept=4.5, linetype=2, size=1)+
  scale_y_continuous(expand=c(0,0))+
  scale_fill_manual(name="Structural Stiffness",labels=c("0 - Soft","1 - Standard","2 - Stiff"), 
                    values=c("burlywood4", "tan", "beige"))+ 
  theme_bw()+
  theme(strip.text.y = element_text(size =12),
        panel.grid=element_blank(),
        legend.position="right")+
  facet_grid(Treatment~.,labeller=labeller(Treatment = facet.labs))

ggsave("figures/Fig5_structural_stiffness.jpg",plot=droop_plot, width=6, height=5)


```


## Figure S1: Max minor ulcers across treatments
```{r, warning=FALSE}
treatlabs = c("12°C", "17°C", "22°C")
names(treatlabs)=c("Control", "Room", "Heat")

ulcers_max = ggplot(data=lesion_max, aes(x=Treatment, y=max_lesions, fill=Treatment))+
  geom_boxplot(outlier.shape= NA, color="black", alpha=0.8)+
  geom_point(alpha=0.5, position=position_dodge2(0.2), color="black")+
  scale_y_continuous(expand=c(0,0), limits = c(-1,13.2))+
  scale_x_discrete(labels=c("12°C", "17°C", "22°C"))+
  scale_fill_manual(values=c("Gold", "Orange","Red"))+
  ylab("Maximum Lesions / Indiv.")+xlab("Treatment")+
  theme_bw()+
  theme(panel.grid=element_blank(), 
        legend.position="none")

ggsave("figures/FigS1_ulcers_max.jpg",plot=ulcers_max, width=6, height=5)


```


## Figure S2 : Correlation between antipredator and structural stiffness
```{r, warning=FALSE}

squeeze_droop_cor = ggplot(data=stiff, aes(x=Squeeze_score, y=Droop_score, color=Treatment))+
  geom_jitter(width=0.1, height=0.1, alpha=0.6)+
  scale_color_manual(labels=c("Control (12°C)","Room (17°C)","Heat (22°C)"), values=c("Gold", "Orange","Red"))+
  theme_bw()+ 
  scale_x_continuous(breaks=seq(0,2.3,1), limits = c(-0.2,2.3))+
  scale_y_continuous(breaks=seq(0,2.3,1), limits = c(-0.2,2.3))+
  xlab("Antipredator Defense") + ylab("Structural Maintenance")+
  theme(strip.text.y = element_text(size =12),
        legend.position="NONE")+
  facet_grid(Treatment~., labeller=labeller(Treatment = facet.labs))

ggsave("figures/FigS2_squeeze_droop_correlation.jpg",plot=squeeze_droop_cor, width=6, height=4)
```


## Figure S3: Model outputs from stiffness models (effect size & 95% CI)
```{r, warning=FALSE}
# First, run models and save model objects (in this case Droop_Top and Squeeze_Top)
# see code above under Stiffness Statistics 
# make output data frame with coefficient and confidene intervals
droop_output = data.frame(coef = coef(Droop_Top), # coef
                          upper = confint(Droop_Top)[,2], # upper CI
                          lower = confint(Droop_Top)[,1], # lower CI
                          stiff = "Structural Maintenance")[-c(1,2),]
squeeze_output = data.frame(coef = coef(Squeeze_Top), # coef
                          upper = confint(Squeeze_Top)[,2], # upper CI
                          lower = confint(Squeeze_Top)[,1], # lower CI
                          stiff= "Antipredator Defense")[-c(1,2),]

stiff_output= rbind(droop_output, squeeze_output) # bind the two outputs together for plotting


stiff_output$Treatment=c("Temp:17°C", "Temp:22°C", "Day 2", # naming treatments (for gg)
                         "Day 3", "Day 4", "Day 5")
stiff_output$Variable = c("Temp", "Temp", "Date", "Date", "Date", "Date")# naming variables (for gg)


# plotting the output
stiffness_output = ggplot(data=stiff_output, aes(x=coef, y=Variable, color=Treatment))+
  geom_point(position=position_dodge(0.8))+
  geom_errorbar(aes(xmin=lower, xmax=upper), size=1, width=0.4, position=position_dodge(0.8))+
  geom_vline(xintercept=0, linetype=2)+
  xlab("Coefficient (Log Odds) ± 95% Confidence Interval")+
  scale_color_manual("Variable Category",values=c("grey30", "grey45", "grey60", "grey75",
                              "goldenrod", "darkorange4"))+
  facet_grid(stiff~.)+
  theme_bw()

ggsave("figures/FigS3_stiffness_model_output.jpg",plot=stiffness_output, width=6, height=4)

```



